Binary companions of red clump stars II: \\ population inference

### 2018-04-09 paper/2-population/twoface-pop.tex
titles
author shit
intro copy pasta

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!
% - Where there are defined math symbols (like \pars), use them!

% other notes
% - Binary engulfment reference: https://arxiv.org/pdf/1002.2216.pdf
% -

@@

\title{Binary companions of red clump stars}

\author{Adrian~M.~Price-Whelan}
\affiliation{Department of Astrophysical Sciences,
             Princeton University, Princeton, NJ 08544, USA}
\email{adrn@astro.princeton.edu}
\correspondingauthor{Adrian M. Price-Whelan}

@@

>>>>

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some
%   bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your
%   arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article
%   or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the
%   same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!
% - Where there are defined math symbols (like \pars), use them!

% other notes
% - Binary engulfment reference: https://arxiv.org/pdf/1002.2216.pdf

@@

\title{Binary companions of red clump stars II: \\
       population inference}

\author[0000-0003-0872-7098]{Adrian~M.~Price-Whelan}
\affiliation{Department of Astrophysical Sciences,
             Princeton University, Princeton, NJ 08544, USA}
\email{adrn@astro.princeton.edu}
\correspondingauthor{Adrian M. Price-Whelan}

@@

Stars typically have companions.
Main sequence stars in the solar neighborhood more often appear in binary or
multiple star systems rather than as solitary stars (e.g.,
\citealt{Duquennoy:1991,Raghavan:2010,Tokovinin:2014,Moe:2017}).
This is likely a generic outcome of star formation, as, for example turbulent
fragmentation in collapsing protostellar clouds can produce stellar multiplets
within length-scales comparable to their spheres of influence (e.g.,
\citealt{Raskutti:2016}).
Binary and multiple star systems are therefore of great interest in
astrophysics: The population of stars and their companions encodes information
about star formation processes, stellar parameters and evolution, and the
dynamics of multi-body systems (for recent reviews, see
\citealt{Duchene:2013,Moe:2017}).

Most of what is known about stellar companions comes from studies of
nearby main-sequence (MS) stars.
Nearly 50\% of MS stars in the solar neighborhood have companions
(e.g., \citealt{Tokovinin:2014}).
MS stars with companions have a large dynamic range of constituent and orbital
characteristics.
For example, binary stars have mass-ratios that span from $\approx 0.03$
to 1 (e.g., \citealt{Kraus:2008}), and have periods from days to
millions of years (e.g., \citealt{Raghavan:2010}).
Less is known about population properties of non-interacting or detached
companions to evolved stars.
